Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-04 paper/paper.tex
reference

Next, several AI models are extracted from various real-life authors from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. For another, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.

@@

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.0787.}
\label{tab:compas_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
Mean Difference     & 0.3282 & 0.2274 & 0.1007 \\
Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 \\
Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 \\
Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 \\
Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 \\
\bottomrule
\end{tabular}
\end{table}

@@

% run this with 100 iter

>>>>

Next, several AI models are extracted from various real-life authors from Kaggle. They are finetuned to perform well on the original dataset. For one, a random forest model is finetuned by searching hyperparameters settings\cite{Ipbyrne2023}. Another random forest model is finetuned with over-sampling methods\cite{Jawat2024}. Also, a logistic regression model is finetuned by performing principal component analysis\cite{Prashant1112023}.

@@

% this 100 experiment is not run yet

With heuristic it is 924m15s. The fit time is 17m1s without heuristic.

@@

\begin{table}[h]
\caption{Fairness measures experiment results of the COMPAS dataset. Average of differences is 0.0787.}
\label{tab:compas_score}
\begin{tabular}{cccc}
\toprule
\textbf{Measure} & \textbf{Original} & \textbf{Synthetic} & \textbf{Difference} \\
\midrule
Demographic Parity  & 0.1310 & 0.0980 & 0.0330 \\
Accuracy Eqaulity   & 0.0079 & 0.0129 & 0.0050 \\
Equalized Odds 1    & 0.0249 & 0.0936 & 0.0687 \\
Equalized Odds 2    & 0.0177 & 0.1016 & 0.0838 \\
Accuracy Equality 1 & 0.1709 & 0.0505 & 0.1203 \\
Accuracy Equality 2 & 0.1695 & 0.0303 & 0.1392 \\
\bottomrule
\end{tabular}
\end{table}

@@

% this is running with 100 iter
